DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-04 rebuttal.tex

\begin{mdframed}[style=comment]
This kind of maps can be created using the gravitational lensing technique [see 29, for review]

- It should be "These" and not "This". "These kind of maps can be created using the gravitational lensing technique [see 29, for review]"
\end{mdframed}
Thank you for spotting this mistake. We updated the manuscript.

\begin{mdframed}[style=comment]
A CNN is composed of the following main building blocks [31]: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, normalization.

- I think that this is generalising a CNN a bit too much. In my mind (and in my personal uses of CNNs) steps (iii) and (iv) are not always necessary either. Perhaps you want to say that you wish to tackle common tasks which often arise in CNNs: i) convolution, (ii) non-linearity, (iii) down-sampling operation, (iv) pooling operation, and (v), optionally, normalisation.
\end{mdframed}
We agree with the reviewer that (iii) and (iv) are also optional. Hence we reformulated this sentence as:
\begin{mdframed}[style=manuscript]
A CNN is composed of the following main building blocks~\cite{lecun1998cnn}:
(i) a convolution,
(ii) a non-linearity.
Optionally, some CNN also have
(iii) a down-sampling operation,
(iv) a pooling operation, and
(v) a normalization.
\end{mdframed}

@@

\begin{mdframed}[style=comment]
The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.

- This is true for supervised learning only and should be stated.
\end{mdframed}
\todo{To check: @michael}
We are not sure this specification is necessary as this cost cannot be computed in an unsupervised setting. We decided to not change the text.
% \nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}

\begin{mdframed}[style=comment]
For global prediction, the cost is as if $N_{pix} = 1$.

- I think this should be "For global prediction $N_{pix} = 1$."
\end{mdframed}
\todo{To check: @michael}

We changed the text as:
\begin{mdframed}[style=manuscript]
For global prediction, we have $N_{pix} = 1$.
\end{mdframed}

@@

This is an interesting observation. The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy. It is convenient that this fact can be used for data augmentation too and make the ML problem solvable even with a small amount of initial simulation. As these two facts are connected, we prefer to leave the sentence as is.

\begin{mdframed}[style=comment]
Probabilities are computed by the SM layer.

- As explained above, these are not probabilities, they are class predictions from the network.
\end{mdframed}
\todo{To check: @michael}
% \nati{Should we simply say "normalized network score"? I do not know...}

We changed the manuscript to:
\begin{mdframed}[style=manuscript]
The normalized network scores are computed by the $SM$ layer.
\end{mdframed}

@@

\begin{mdframed}[style=comment]
We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
\end{mdframed}
% \todo{Assign: @nati, @michael}
% \nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
We updated the section with a citation and some extra information.
\begin{mdframed}[style=manuscript]
We derived this rule from the Chebyshev polynomial equations and some empirical experiments. Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.
\end{mdframed}

\begin{mdframed}[style=comment]
Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
\end{mdframed}
\todo{Assign: @all}
% \nati{The problem is that random filters are picky as well and look very similar. Should we say that? I do not think a colorbar is necessary since there are numbered axes on the top plots. Do you agree?}
% \TK{Added sentence}

We decided not to add a colorbar as scale information is already present in the top plot of the figure.
We added a small explanation for the peak structure
\begin{mdframed}[style=manuscript]
The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
\end{mdframed}

@@

\begin{mdframed}[style=comment]
Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.

- What does "this" refer to?
\end{mdframed}
We have clarifed the sentence as:
\begin{mdframed}[style=manuscript]
Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling.
\end{mdframed}

\begin{mdframed}[style=comment]
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

- I think it might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable. If I were you I'd move this into the main body of the paper.
\end{mdframed}
We thank the reviewer for this suggestion. We agree it is an important point, especially when one discuss the rotation equivariance. Nevertheless, since almost all of this discussion is done in Appendix, it complicated to bring it to the main body of the paper without moving a significant part of the Appendix as well.
\todo{To check: @all}

### 2019-03-04 scnn.tex
fix last comments

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
(i) a convolution,
(ii) a non-linearity,
(iii) a down-sampling operation,
(iv) a pooling operation, and
(v), optionally,  normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}. As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations, however, need to be generalized from Euclidean domains to the sphere.

@@

The cost (or loss) function $C(\Y, \bar \Y) = C(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$. For a classification task, the cost is usually taken to be the cross-entropy
\begin{equation*}
	C(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
\end{equation*}
where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise. For global prediction, the cost is as if $N_{pix} = 1$.
For a regression task, a common choice is the mean squared error (MSE)
\begin{equation*}
	C(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
\end{equation*}
where $\bar{\Y}$ is the desired output. Again, take $N_{pix} = 1$ for global regression. We emphasize that the cost function and the $SM$ layer are the sole differences between a neural network engineered for classification or regression.

@@

\nati{
Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2DCNN).
To do so, the samples are first transformed into a square image before being fed into the 2DCNN.
As described in \ref{sec:projection}, we use the geometrical properties of HEALPix to construct an efficient and simple projection of the samples.
Note that during the review process another spherical CNN architecture using exploiting this property appeared \cite{krachmalnicoff2019convolutional}.
We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2DCNN.
}
\nati{Say something about the number of parameters/fitlers. }

>>>>

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
(i) a convolution,
(ii) a non-linearity.
Optionally, some CNN also have
(iii) a down-sampling operation,
(iv) a pooling operation, and
(v) a normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}. As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations, however, need to be generalized from Euclidean domains to the sphere.

@@

The cost (or loss) function $C(\Y, \bar \Y) = C(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$. For a classification task, the cost is usually taken to be the cross-entropy
\begin{equation*}
	C(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
\end{equation*}
where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise. 
For global prediction, we have $N_{pix} = 1$.
For a regression task, a common choice is the mean squared error (MSE)
\begin{equation*}
	C(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
\end{equation*}
where $\bar{\Y}$ is the desired output. Again, take $N_{pix} = 1$ for global regression. We emphasize that the cost function and the $SM$ layer are the sole differences between a neural network engineered for classification or regression.

@@

\nati{
Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2DCNN).
To do so, the samples are first transformed into a square image before being fed into the 2DCNN.
As described in \ref{sec:projection}, we use the geometrical properties of HEALPix to construct an efficient and simple projection of the samples.
Note that during the review process another spherical CNN architecture using exploiting this property appeared \cite{krachmalnicoff2019convolutional}.
We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2DCNN.
}
